\documentclass{res}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{times}
\usepackage{qrcode}
\usepackage{enumitem}
\setlist{nosep}
\usepackage[lmargin=0.5in, rmargin=1in, tmargin=0.25in, bmargin=0.25in]{geometry}
\pagestyle{empty}
\setlength{\textheight}{10.5in}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\begin{document}
\begin{resume}
\begin{changemargin}{-0.5in}{0in}
	\begin{center}
		\begin{Huge}
		\textbf{Daniel R. Murtha}
		\end{Huge}
	\\
		\begin{normalsize}
			5445 Foxridge Drive Apt 308, Mission KS, 66202\\
			M: (913) 775-3507~~~~~~E: dr.murtha@me.com
		\end{normalsize}
	\end{center}
\end{changemargin}\vspace{-5pt}
 \section{Skills:}\vspace{-10pt}
 \begin{minipage}{0.8\linewidth}
 	\begin{small}
 		\begin{flushleft}
 			{\bf Computer: }C\# .Net Core/Framework, C++, JavaScript, SQL/PostgreSQL, Python, Java, Haskell\\
			{\bf Other: } Eagle Scout, AWS Cloud Development, Embedded Systems, Profession Scrum Master I, Japanese, HAM Radio Tech
 		\end{flushleft}
 	\end{small}   
 \end{minipage}
 \begin{minipage}{0.2\linewidth}
 	\begin{small}   
		\begin{flushright}
			github.com/Demonslyr\\
			\qrcode{https://github.com/Demonslyr}
		\end{flushright}     
 	\end{small}   
 \end{minipage}\vspace{-10pt}
 
\section{Education:}\vspace{5pt}
\begin{minipage}{0.8\linewidth}
	\begin{small}
		\begin{flushleft}
			University of Kansas; Bachelor of Science in Computer Engineering GPA: 3.33\\Kansas City Kansas Community College; Associates of Science\\J.F. Obirin; Study Abroad - Intensive Japanese Language Study
		\end{flushleft}
	\end{small}   
\end{minipage}
\begin{minipage}{0.2\linewidth}
	\begin{small}   
		\begin{flushright}
			Graduated 2016\\Graduated 2010\\Summer 2016
		\end{flushright}
	\end{small}   
\end{minipage}\vspace{-10pt}
 
\section{Professional Experience:}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{5.5in}\= \kill 
    {\bf VinSolutions, Software Engineer I,II} \>~~~~~~~~~~~~~Aug 2016 - Present\\
    Mission, KS 66202
   \end{tabbing}\vspace{-10pt}
	\begin{itemize}
		\item Owned and expanded a developer portal, used by 18 dev teams, which managed the process of application deployments and provided a dashboard with a near real-time overview and history of deployments and app automation.
		\item Took initiative to build a service layer for the developer portal to replace the integration with Zapier which increased portal responsiveness and reduced costs paid to Zapier.
		\item Worked with my team to develop the companies first cloud based content management system for storing and serving terabytes of data to handle an ever increasing demand that would overwhelm the company's hardware.
		\item Developed, with my team, multiple integrations with third parties and sister business units to unify previously desparate user experiences across the company's userfacing products. \vspace{-15pt}
	\end{itemize}
   \begin{tabbing}
	\hspace{5.5in}\= \kill 
	{\bf VinSolutions, Software Engineering Intern} \>~~~~~~~~May 2015 - June 2016\\
	Mission, KS 66202
	\end{tabbing}\vspace{-10pt}
	\begin{itemize}
		\item Developed .Net web application to help automate manual deployments saving lost developer time.
		\item Worked in an AGILE development team to maintain the VinSolutions CRM.\vspace{-15pt}
	\end{itemize}
   \begin{tabbing}
   \hspace{5.5in}\= \kill
    {\bf University of Kansas, Undergraduate Research Assistant} \>~~~~~~~~June 2014 - May 2015\\
    Lawrence, KS 66045
   \end{tabbing}\vspace{-10pt}
	\begin{itemize}
		\item Helped to replace FPGA based UAV radar signal processing system with an Nvidia Tegra K1 microprocessor.
		\item Developed a multi-threaded signal processing pipeline utilizing Boost and FFTW v3 libraries in C++.
		\item Performed benchmarking and pipeline optimization on code to meet real-time performance benchmarks.\vspace{-15pt}
	\end{itemize}
   \begin{tabbing}
   \hspace{5.5in}\= \kill
   {\bf University of Kansas School of Engineering EECS Shop, Senior Student Hire}  \>~~~~~March 2014 - May 2015\\
   Lawrence, KS 66045
   \end{tabbing}\vspace{-10pt}
	\begin{itemize}
		\item Operated and maintained the LPKF Circuit mill and provide technical support for Cadence/PSPICE.
		\item Maintained engineering labs and performed life-cycle replacements for hundreds of EECS workstations.
		\item Received and track shop inventory.
		\item Trained new and managed current student hires.\vspace{-15pt}
	\end{itemize}
   \begin{tabbing}
	\hspace{5.5in}\= \kill
	{\bf Chief Information Office (G6), Computer Technician}  \>~~~~~~July 2012 - March 2013\\
	Fort Leavenworth, KS 66027
\end{tabbing}\vspace{-10pt}
	\begin{itemize}
		\item Department of Defense Secret clearance.
		\item Performed data recovery on users' computers; restoring their files to operations.
		\item Conducted training for users on multiple devices and subjects.
		\item Performed tasks involving Hardware/Software troubleshooting, SCCM management, System building, and Life Cycle Replacement.\vspace{-10pt}
	\end{itemize}

\section{Projects:}          
{
	\textbf{JSho:} A JavaScript-based arcade style bullet swarm game utilizing HTML 5 canvas.\\
	\textbf{RealViz:} A spectrum analyzer visualization for streaming. Utilizes the Minum library with Processing2 on top of Java to generate real-time visualizer from audio inputs using Fourier transforms.\\
	\textbf{UAV Radar Detection:} Augment UAV flight computer with object detection/tracking and collision avoidance utilizing an NVIDIA Tegra K1.\\
	\textbf{Dev Ops FileSync:} C\# .Net application to sync Dev and QA servers for application deployments at manual intervals or by automatic schedule.\\
	\textbf{Unnamed Project:} React native mobile application to support professional and amateur mixologists with a backend hosted in kubernetes.
}
\end{resume}
\end{document}